Mood increases during video game play: A naturalistic observational case study of PowerWash Simulator

### 2023-09-04 ms.qmd
Fix metadata

---
date: 2023-07-18
bibliography: bibliography.bib
format:
  html: default
---

>>>>

---
title: "Mood increases during video game play: A naturalistic observational case study of PowerWash Simulator"
description: Computational notebook supporting our manuscript
author:
  - name: Matti Vuorre
    orcid: 0000-0001-5052-066X
    email: mjvuorre@uvt.nl
    url: https://vuorre.netlify.app
    affiliation:
      - ref: a
      - ref: b
  - name: Nick Ballou
    orcid: 0000-0003-4126-0696
    affiliation:
      - ref: b
  - name: Andrew K. Przybylski
    orcid: 0000-0001-5547-2185
    affiliation:
      - ref: b
affiliations:
  - id: a
    name: Tilburg University
  - id: b
    name: University of Oxford

date: 2023-09-04
bibliography: bibliography.bib
format:
  docx: default
  html: default
---
